A thesis draft

### 2018-11-28 res/sections/20-VNFImplementaton.tex
Finish SFC implementation

>>>>

In this context our chain has the ability to perform packet classification,
making the whole system able to separate the traffic based on a packet-type
policy.

Another important aspect to keep in consideration is how communications inside
the chain are performed. The packet arriving in the ingress needs to be
perserved, so that VNFs can perform packet elaboration. In order to otain this,
packet encapsulation has been used. IP in IP encapsulation allow to preserve the
original packet, making the incoming packet the payload of a new one.

Ironhide, which was introduced in the previous chapter, plays a crucial role in
the establishment of a end-to-end connection between the client and the
receiver. Ironhide is able to fulfill the ingress and the egress role, and it
provides the necessary tools to add and remove the SFC headers that gets appended
and removed.

Finally, we were able to create bidirectional chains, resistent to faults and
degradations that saddisfty the defined requirements.
